---
title: "Prediction of Catalogue Orders (R)"
author: "Adela Dai"
output: pdf_document
---

# Dataset
The dataset `cat_buy.rda` contains data on the response of customers to the mailing of spring catalogues.  The variable `buytabw` is `1` if there is an order from this spring catalogue and `0` if not.  This is the dependent or response variable.  

This spring catalogue was called a "tabloid" in the industry. The catalogue featured women's clothing and shoes. The independent variables represent information gathered from the internal `house file` of the past order activity of these 20,617 customers who received this catalogue.  

In direct marketing, the predictor variables are typically of the "RFM" type: 1. Recency 2. Frequency and 3. Monetary value. This data set has both information on the volume of past orders as well as the recency of these orders. 

The variables are:

* tabordrs  (total orders from past tabloids) 

* divsords  (total orders of shoes in past)  

* divwords  (total orders of women's clothes in past)  

* spgtabord (total orders from past spring cats)  

* moslsdvs  (mos since last shoe order)  

* moslsdvw  (mos since last women's clothes order)  

* moslstab  (mos since last tabloid order)  

* orders    (total orders) 

## Randomly sample and divide data into two parts
```{r}
load('cat_buy.rda')

obs = nrow(cat_buy)
set.seed(10)
ind.est = sample(1 : obs, obs / 2)

est_sample = cat_buy[ind.est, ]
holdout_sample = cat_buy[-ind.est, ]
```

## Fit a logistic regression model using the estimation sample
First I run a logistic regression on all of the variables.
```{r}
lregB1 = glm(buytabw ~., data = est_sample, family = binomial)
summary(lregB1)
```
Since `divsords` is insignificant, I remove the variable and fit a reduced model.

```{r}
lregB2 = glm(buytabw ~. - divsords, data = est_sample, family = binomial)
summary(lregB2)
```
As AIC reduced, this model produced a better model fit.

The fitted model suggests the following:

* More orders increase probability of purchase (at least for `tabordrs`, `divwords`, and `spgtabord`). This is intuitive.

* As time since last order increases, purchase probability decreases (`moslsdvs`, `moslsdvw`, `moslstab`). This is intuitive.

* More total orders (orders) decreases the probability of purchase. This contradicts the first finding and is counter-intuitive.

## Plot the correlation matrix and chart
```{r}
round(cor(est_sample), 2)
```

```{r}
pairs(~ tabordrs + divwords + spgtabord + orders, data = est_sample, 
      main = 'Correlations', col = '#2774AE')
```

The correlation matrix and plot show that there is correlation between some variables, e.g. `tabordrs` and `spgtabord`. However, this is not an issue as the correlation is not huge.

## Use the best-fit to predict using the holdout sample  
```{r}
phat = predict(lregB2, new = holdout_sample, type = 'response')
```

## Plot boxplots of the fitted probabilities
```{r}
library(ggplot2)

qplot(factor(holdout_sample$buytabw), phat, geom = 'boxplot', fill = I('#2774AE'), 
      xlab = 'buytabw') +
  ggtitle('Distribution of Fitted Probabilities by Buytabw') +
  theme(axis.title = element_text(size = rel(1.5)), 
        axis.text = element_text(size = rel(1.25)))
```

## Compute a "lift" table
```{r}
deciles = cut(phat, breaks = quantile(phat, probs = c(seq(from = 0, to = 1, by = .1))),
              include.lowest = TRUE)
deciles = as.numeric(deciles)

df = data.frame(deciles = deciles, phat = phat, buytabw = holdout_sample$buytabw)

lift = aggregate(df, by = list(deciles), FUN = 'mean', data = df)
lift = lift[, c(2, 4)]
lift[, 3] = lift[, 2] / mean(holdout_sample$buytabw)
names(lift) = c('decile', 'Mean Response', 'Lift Factor')
lift
```